Millions of Type Errors

### 2023-08-30 programming23/paper.tex
related work, diff private trace analysis
row distro data, quick plot
timeline plot

\begin{figure}[t]
  \includegraphics{img/row-distribution.pdf}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California.}
  \label{f:records-per-hour}
\end{figure}

@@

>>>>

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{img/row-distribution.pdf}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California. Shaded regions correspond to weekends.}
  \label{f:records-per-hour}
\end{figure}

@@

Differential privacy for coverage analysis of software traces,
adds noise to traces,
hard because infinitely many traces,
use CFG abstraction of possible behaviors for callgraph analysis,
count sketch data structure~\cite{hlzbr-ecoop-2021}.

other Nasko papers:
https://dblp.org/pid/83/1412.html
